Excitation functions for (p,x) reactions of niobium in the energy range of E\texorpdfstring{$_{\text{p}}$\,=\,40--90\,}{Ep = 40--90 }MeV

### 2018-05-12 nb_px_paper/Response_to_Reviewers.tex

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage[ampersand]{easylist}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{amsmath}

\newfloat{figure}{htbp}{figs}

% \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
\newcommand{\colornote}[1]{\textcolor{red}{#1}}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\pp}[1]{\left( #1\right)}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Mark Breese, PhD \\
Editor \\
Nuclear Instruments and Methods in Physics Research Section B: \\
Beam Interactions with Materials and Atoms}

\begin{flushleft}
{\large\bf Andrew S. Voyles}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill The University of California, Berkeley \\
\hfill 1106B Etcheverry Hall, Berkeley, CA  94720-1730 \\
\hfill (850) 281-0217 or (510) 486-7310 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Dr. Breese,}

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Excitation functions for (p,x) reactions of niobium in the energy range of E\texorpdfstring{$_{\text{p}}$\,=\,40--90\,}{Ep = 40--90 }MeV}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.  Please find my responses detailed in \colornote{red text.}

  \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.  We would especially like to thank the referees for their thorough reading and critique, which has made it a better paper. Their comments were very constructive and pointed out some valuable improvements.

  Please find the feedback following here, and our revised manuscript attached.

  Sincerely yours,\\ \\ \\ \\ Andrew S. Voyles

% \closing{Sincerely yours,}

  \vfill

 \pagebreak

 Reviewer \#1:

 Authors have reported excitation function of the proton induced nuclear reactions on niobium. Details on experimental techniques, data analysis and error calculations related to cross section measurements are given.

The work is interesting to get standard reaction, isotope production and radiation safety analysis. The results will rich the data bank. Authors emphasized on the 93Nb(p,4n)90Mo reaction because of its importance as monitor reaction.

However, this work reported cross sections only at six energies, which are also not consistent with the model calculations in many cases. The results of this work are not sufficient to extract standard data as well as to establish 93Nb(p,4n)90Mo as monitor reaction. Therefore, title of the paper should be changed to \enquote{Excitation functions for (p,xn) reactions of niobium in the energy range of Ep= 40-90 MeV}.

 \colornote{We thank the reviewer for their thoughtful comments, and the excellent suggestion for shifting the title to reflect the broader scope of work covered by this manuscript.  We would, however, respectfully suggest that the title should become \enquote{Excitation functions for (p,x) reactions on niobium in the energy range of Ep= 40-90 MeV}, as \enquote{(p,xn)} typically refers to reactions where only neutrons are secondaries, and many of the reactions we measured  include charged particles in the exit channel.}

%   \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

As mentioned in section 2, authors have performed a single irradiation. Therefore, in section 4 (Conclusion), "\ldots 38 measurements of cross sections\ldots." and "\ldots five independent measurements of isomer \ldots." are wrong. It should be corrected.

\colornote{We  thank the reviewer for their  correction, as our language incorrectly implied multiple measurements instead of multiple reported cross sections arising from a single measurement. We have corrected this language to "\ldots  measurements of 38 cross sections\ldots." and "\ldots  independent measurements of five isomer \ldots."}

The manuscript in well written and I would like to recommend this paper to accept for publication in NIMB after the above corrections.

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2018-05-12 nb_px_paper/nb_body_text.tex
Changed title and some conclusion langauge, following reviewer feedback.  Resubmitted as 1st revision.

We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
Nearly all cross sections have been reported with higher precision than previous measurements.
We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

>>>>

We present here a set of measurements of 38 cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as  independent measurements of five isomer branching ratios.
Nearly all cross sections have been reported with higher precision than previous measurements.
We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

### 2018-05-12 nb_px_paper/nb_px_paper.tex
Pushing fix for missing /mmicro macro?
Changed title and some conclusion langauge, following reviewer feedback.  Resubmitted as 1st revision.

%% Give the name of the journal
\journalname{Nuclear Instruments and Methods in Physics Research B}

@@

@@

% % \collaboration{MUSO Collaboration}%\noaffiliation
% % 
% % \author{Charlie Author}
% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
% % \affiliation{
% %  Second institution and/or address\\
% %  This line break forced% with \\
% % }%
% % \affiliation{
% %  Third institution, the second for Charlie Author
% % }%
% % \author{Delta Author}
% % \affiliation{%
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% % }%
% % 
% % \collaboration{CLEO Collaboration}%\noaffiliation
% 
% \date{\today}% It is always \today, today,
%              %  but any date may be explicitly specified
% 
% %% Title, authors and addresses
% 
% %% use the tnoteref command within \title for footnotes;
% %% use the tnotetext command for the associated footnote;
% %% use the fnref command within \author or \address for footnotes;
% %% use the fntext command for the associated footnote;
% %% use the corref command within \author for corresponding author footnotes;
% %% use the cortext command for the associated footnote;
% %% use the ead command for the email address,
% %% and the form \ead[url] for the home page:
% %%
\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}

@@

We gratefully acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics. 
This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy
Additional support has been provided by the U.S. Nuclear Regulatory Commission.

>>>>

%% Give the name of the journal
\journalname{Nuclear Instrum. and Methods in Phys. Res. B}

@@

% Sick of fighting siunitx - consistent text micro symbol
% DO NOT uncomment this!!! or else broken unicode (Âţ)
% \sisetup{math-micro=\text{µ},text-micro=µ}
% \si\micro
\newcommand{\mmicro}{\si\micro}

\usepackage{adjustbox}

@@

% % \collaboration{MUSO Collaboration}%\noaffiliation
% % 
% % \author{Charlie Author}
% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
% % \affiliation{
% %  Second institution and/or address\\
% %  This line break forced% with \\
% % }%
% % \affiliation{
% %  Third institution, the second for Charlie Author
% % }%
% % \author{Delta Author}
% % \affiliation{%
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% % }%
% % 
% % \collaboration{CLEO Collaboration}%\noaffiliation
% 
% \date{\today}% It is always \today, today,
%              %  but any date may be explicitly specified
% 
% %% Title, authors and addresses
% 
% %% use the tnoteref command within \title for footnotes;
% %% use the tnotetext command for the associated footnote;
% %% use the fnref command within \author or \address for footnotes;
% %% use the fntext command for the associated footnote;
% %% use the corref command within \author for corresponding author footnotes;
% %% use the cortext command for the associated footnote;
% %% use the ead command for the email address,
% %% and the form \ead[url] for the home page:
% %%

% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}
\title{Excitation functions for (p,x) reactions of niobium in the energy range of E\texorpdfstring{$_{\text{p}}$\,=\,40--90\,}{Ep = 40--90 }MeV}
% ):  development of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as an intermediate-energy proton monitor}

@@

We gratefully acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics. 
This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy.
Additional support has been provided by the U.S. Nuclear Regulatory Commission.
